Output Summary

### 2023-05-04 03-post-process/output-plots-children/05-length.Rmd

#### Realized & Predicted

@@

>>>>

#### Realized & Expected

The `r colorize("realized time series", main_cols["model"])` and `r colorize("expected time series", main_cols["model2"])` (i.e., without process noise).

@@

The `r colorize("realized time series", main_cols["model"])` and the `r colorize("ratio between observed smolt and parr mean length", main_cols["model2"])`.

### 2023-05-04 03-post-process/output-plots-children/08-misc-process-model.Rmd

```{r pi-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
```

@@

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
ocean_surv_plot = function(j) {
  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
  mtext(side = 2, outer = T, line = 0, "Survival")
}
```

### CAT

```{r}
ocean_surv_plot(j_cat)
```

### LOS

```{r}
ocean_surv_plot(j_los)
```

### MIN

```{r}
ocean_surv_plot(j_min)
```

### UGR

```{r}
ocean_surv_plot(j_ugr)
```

@@

```{r maturity-plot-fn}
maturity_plot = function(j) {
  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))

  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
}
```

### CAT

```{r maturity-cat, fig.width = 6, fig.height = 5}
maturity_plot(j_cat)
```

### LOS

```{r maturity-los, fig.width = 6, fig.height = 5}
maturity_plot(j_los)
```

### MIN

```{r maturity-min, fig.width = 6, fig.height = 5}
maturity_plot(j_min)
```

### UGR

```{r maturity-ugr, fig.width = 6, fig.height = 5}
maturity_plot(j_ugr)
```

@@

```{r n-stray, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Number of Strays Entering Population")
```

@@

```{r stray-comp, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))

  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
}

par(mfrow = c(2,2), oma = c(0,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
```

>>>>

```{r pi-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               label_text = pops[j], yrs = all_yrs[ts_yrs])
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Proportion of Parr with Fall Migration Strategy")
```

@@

### Yr1 {.tabset .tabset-pills}

#### NOR {.tabset .tabset-pills}

##### Realized Alone

The `r colorize("realized time series", main_cols["model"])`.

```{r phi-O0-O1-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
```

##### Realized & [Expected + AR(1)]

The `r colorize("realized time series", main_cols["model"])` and the `r colorize("expected time series including the carry-over residual", main_cols["model2"])`.

```{r phi-O0-O1-plots2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))

  keep = sub_index("^phi_O0_O1_dot2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  add_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs])
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr1 Ocean Survival (NOR)")
```

#### HOR {.tabset .tabset-pills}

##### Realized Alone

The `r colorize("realized time series", main_cols["model"])`.

```{r phi-O0-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr1 Ocean Survival (HOR)")
```

### Yr2 {.tabset .tabset-pills}

#### NOR

```{r phi-O1-O2-nor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr2 Ocean Survival (NOR)")
```

#### HOR

```{r phi-O1-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr2 Ocean Survival (HOR)")
```

### Yr3 {.tabset .tabset-pills}

#### NOR

```{r phi-O2-O3-nor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr3 Ocean Survival (NOR)")
```

#### HOR

```{r phi-O2-O3-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Yr3 Ocean Survival (HOR)")
```

@@

### Pr(Age-3) {.tabset .tabset-pills}

#### NOR

```{r psi-O1-nor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Pr(Mature Age-3|NOR)")
```

#### HOR

```{r psi-O1-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = c(0, 0.4))
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Pr(Mature Age-3|HOR)")
```

### Pr(Age-4) {.tabset .tabset-pills}

#### NOR

```{r psi-O2-nor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Pr(Mature Age-4|NOR)")
```

#### HOR

```{r psi-O2-hor-plots, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(est = post_summ(post, keep), yrs = all_yrs[ts_yrs], label_text = pops[j], ylim = ylim_01)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Pr(Mature Age-4|HOR)")
```

@@

```{r n-stray, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("^G[year,origin,pop]", pop = j, year = ts_yrs, origin = o_hor)), yrs = all_yrs[ts_yrs], label_text = pops[j])
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Return Year", "Number of Strays Entering Population")
```

@@

```{r stray-comp, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  x = post_summ(post, sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = j))

  mp = barplot(x["mean",], ylim = ylim_01, xaxt = "n", col = tran_cols["model"], border = main_cols["model"])
  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 1)
  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
  segments(par("usr")[1], par("usr")[3], par("usr")[1], par("usr")[4], xpd = TRUE, col = par("col.axis"))
  panel_label(pops[j])
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Age of Return", "Proportion of Strays by Age")
```

### 2023-05-04 03-post-process/output-plots.Rmd

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
knitr::opts_knit$set(root.dir = "C:/Users/bstaton/Desktop/Staton/1_critfc/analyses/GR-sslcm/03-post-process")
```

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "test-rmd_vshort"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

```{r directories, include = FALSE}
# set root directory to the project directory: one level up from this location
knitr::opts_knit$set(root.dir = "C:/Users/bstaton/Desktop/Staton/1_critfc/analyses/GR-sslcm/03-post-process")
```
